Multi-modal spatial availability: a research proposal

### 2023-06-12 CIT-Presentation.Rmd
Draft CIT-Presentation 2 (resolved some figure formating issues)

---
title: "Multi-modal spatial availability: a research proposal"
subtitle: "CIT - Tenerife 2023"
author: "Anastasia Soukhov, J. Tarriño Ortiz, J. A. Soria-Lara, A. Páez"
date: "2022-11-10"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current% / 12" 
      highlightStyle: github
      highlightLines: true
      ratio: '16:9'
      countIncrementalSlides: false
      beforeInit: "macros.js"
---
```{r xaringan-themer, include=FALSE, warning=FALSE}
#this themer package allows us to change the .css themes through this chunk. Easier than changing the .css directly.
library(xaringanthemer)
style_mono_accent(
  base_color = "#7A003C", #maroon
  link_color = "#5E6A71", #grey
  text_bold_color = "#FDBF57", #gold
  text_slide_number_color = "#FDBF57", #gold
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

@@

```{r, create-figure-with-toy-example, echo=FALSE, eval=FALSE}
toy_example_plot <- ggplot() + 
  # Plot centers
  geom_circle(data = centers,
             aes(x0 = x, 
                 y0 = y,
                 r = radius),
             color = "grey40") +
  annotate(geom = "label", 
           x=c(0.5, 0.6, 7),
           y=c(9, 1, 5.2), 
           label = c("Suburban", "Urban", "Satellite"), 
           size=4, 
           label.size=NA) +
  # Connect origins and destinations with curves
  geom_curve(data = od_lines,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend,
                   linetype = group,
                   group = group),
             curvature = 0.20,
             linewidth = 1,
             color = "black") +
  # Text on curves
  geom_textcurve(data = od_lines,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend,
                   linetype = group,
                   group = group,
                   label = time),
               size = 3,
             curvature = 0.20,
             color = "black") +
  # Plot origins and destinations
  geom_point(data = od,
            aes(size = size,
                x = x, 
                y = y, 
                color = type,
                shape = type)) +
  scale_size(range = c(4, 10)) +
  # Label origins and destinations
  geom_text(data = od, 
            aes(x, 
                y, 
                label=id), 
            size=3) +
  # Create table
  annotate(geom = "table",
           x = 9, 
           y = 9, 
           label = list(od_table),
           fill = "white",
           size=3) +
  # Theme the plot
  coord_fixed() + 
  theme_void() + guides(shape = "none", size = "none", color = "none", linetype ="none")

@@

$$A_i^m = \sum_{j}O_jf(c_{ij})^m$$
-   $i$ is a set of origin locations
-   $j$ is a set of destination locations
-   $O_j$ is the number of opportunities at location $j$
-   $f(\cdot)$ is an impedance function of $c_{ij}$ (cost of moving between $i$ and $j$) for each mode $m$

**E.g.**, used in _(Tahmasbi et al., 2019)_.

@@

Does not include competition (demand:supply or the mass effect) _(Shen, 1998; Merlin and Hu, 2018)_.

@@

**e.g.**, used in _(Tahmasbi et al., 2019)_ for quantify access $A_i$ for $m$ walking, public transit, and private car modes to retail store destinations (different $f^m(c_{ij}^m)$ for each $m$)
- Suffers from the same interpretability issues _(Handy and Niemeier, 1997; Miller et al., 2018)_
- Does not include competition (demand:supply or the mass effect) _(Shen, 1998; Merlin and Hu, 2018)_

.pull-right[
]

@@

---
count: false
## Multi-modal accessibility measures

.pull-left[
#### Competitive accessibility (Shen-type) - no proportional allocation
Shen (1998) modified Hansen-type accessibility; popularized as the **two-step floating catchment approach (2SFCA)** by _(Luo and Wang, 2003)_

@@

It considers multi-model competition following the generalized:
$$S_i = \sum_m \biggl(\frac{P_i^m}{P_i}\biggr) \sum_j \frac{O_jf(c_{ij})^m}{\sum_m \sum_i P_{i}^m f(c_{ij})^m}$$

@@

However, the resulting value is an accessibility _score_ so interpretation is obfuscated _(Soukhov et al., 2023)_

@@

.right-column[
```{r comparison-impedance-functions-synthetic-example1, echo=FALSE, warning=FALSE, fig.width=9, fig.height=6}
data.frame(tt = seq(0, 100, 1)) %>%
  mutate(f1 = exp(-0.1 * tt)) %>%
  pivot_longer(cols = -tt,
               names_to = "Function",
               values_to = "f") %>%
  mutate(Function = case_when(Function == "f1" ~ "beta = 0.1")) %>%
  ggplot() +
  xlab(expression(c[ij]~"(travel time in minutes)")) +
  ylab(expression('f(c'[ij]*')')) +
  geom_line(aes(x = tt, 
                y = f,
                color = Function), size=1) +
  scale_color_manual(values = c("dark green"), label = c(expression("exp(-0.1 c"[ij]*")")))+
  scale_x_continuous(breaks = seq(0, 80, 20))+
  theme_minimal()+
  theme(axis.title = element_text(size=18),
        axis.text = element_text(size=16),
        legend.position = c(0.85, 0.9),
        legend.title = element_blank(),
        legend.text = element_text(size=18))
```
]

@@

.right-column[
```{r comparison-impedance-functions-synthetic-example2, warning=FALSE, echo=FALSE, fig.width=9, fig.height=6}
data.frame(tt = seq(0, 100, 1)) %>%
  mutate(f1 = exp(-0.1 * tt),
         f2 = exp(-0.6 * tt)) %>%
  pivot_longer(cols = -tt,
               names_to = "Function",
               values_to = "f") %>%
  mutate(Function = case_when(Function == "f1" ~ "beta = 0.1",
                              Function == "f2" ~ "beta = 0.6")) %>%
  ggplot() +
  xlab(expression(c[ij]~"(travel time in minutes)")) +
  ylab(expression('f(c'[ij]*')')) +
  geom_line(aes(x = tt, 
                y = f,
                color = Function), size=1) +
  scale_color_manual(values = c("dark green", "#9999CC"), label = c(expression("exp(-0.1 c"[ij]*")"), expression("exp(-0.6 c"[ij]*")")))+
  scale_x_continuous(breaks = seq(0, 80, 20))+
  theme_minimal()+
  theme(axis.title = element_text(size=18),
        axis.text = element_text(size=16),
        legend.position = c(0.85, 0.9),
        legend.title = element_blank(),
        legend.text = element_text(size=18))
```
]

---
### Simulated example - Hansen-type accessibility (no competition or proportional allocation consideration)

@@

@@

.pull-right[
$S_i = \sum_m \biggl(\frac{P_i^m}{P_i}\biggr) \sum_j \frac{O_j f(c_{ij})^m}{\sum_m \sum_i P_{i}^m f(c_{ij})^m}$:
```{r, echo=FALSE, message=FALSE}
S <- S_m %>%
  group_by(i) |>
  summarize(S = sum(pop*S)/sum(pop),
            .groups = "drop")

@@

- Spatial availability per origin and mode:

$V^m_{i} = \sum_{j=1}^J O_j\ F^{t,m}_{ij}$

@@

- Spatial availability per origin:

$V_{i} = \sum_{m=1}^M V^m_{i}$

- Considers **competition** and **proportionally allocates opportunities** (singly-constrained: $O = \sum_{j=1}^J O_j$)
]
???

- So let me introduce spatial availability, it consists of proportional allocation factors and the opportunities. the population allocation factor is the allocation of opportunities, proportional to the population size. It is always a proportion between 0 to 1.

@@

$V^m_{i} = \sum_{j=1}^J O_j\ F^{t,m}_{ij}$ and $\frac{V^m_{i}}{P_{i}^m}$

@@

.pull-right[
$S_i$ (eqv. to $\frac{V_i}{P_i}$) and $V_{i} = \sum_{m=1}^M V^m_{i}$

@@

.pull-left[
```{r, echo=FALSE, out.width='80%',fig.align='center'}
knitr::include_graphics("Presentations/SA_i_V_zn1259_plot.png")
```
Spatial Availability $V_i$ at resolution Zona 1259
]

.pull-right[
```{r, echo=FALSE, out.width='80%', fig.align='center'}
knitr::include_graphics("Presentations/SA_i_V_zn208_plot.png")
```
Spatial Availability $V_i$ at resolution Zona 208
]

@@

---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='70%',fig.align='center'}
knitr::include_graphics("Presentations/SA_im_vv_zn1259_plot.png")
```
Spatial Availability by $m$ population ( $v_i^m$ ) at resolution Zona 1259

@@

>>>>

---
title: "Multi-modal spatial availability: a research proposal"
subtitle: "CIT - Tenerife 2023"
author: "Anastasia Soukhov, J. Tarriño Ortiz, J. A. Soria-Lara, A. Páez"
date: "2022-11-10"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current% / 14" 
      highlightStyle: github
      highlightLines: true
      ratio: '16:9'
      countIncrementalSlides: false
      beforeInit: "macros.js"
---
```{r xaringan-themer, include=FALSE, warning=FALSE}
#this themer package allows us to change the .css themes through this chunk. Easier than changing the .css directly.
library(xaringanthemer)
style_mono_accent(
  base_color = "#7A003C", #maroon
  link_color = "#5E6A71", #grey
  text_bold_color = "#FDBF57", #gold
  text_slide_number_color = "#FDBF57", #gold
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

@@

```{r, create-figure-with-toy-example, echo=FALSE, eval=FALSE}
toy_example_plot <- ggplot() + 
  # Plot centers
  geom_circle(data = centers,
             aes(x0 = x, 
                 y0 = y,
                 r = radius),
             color = "grey40") +
  annotate(geom = "label", 
           x=c(0.5, 0.6, 7),
           y=c(9, 1, 5.2), 
           label = c("Suburban", "Urban", "Satellite"), 
           size=4, 
           label.size=NA) +
  # Connect origins and destinations with curves
  geom_curve(data = od_lines,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend,
                   linetype = group,
                   group = group),
             curvature = 0.20,
             linewidth = 1,
             color = "black") +
  # Text on curves
  geom_textcurve(data = od_lines,
               aes(x = x,
                   y = y,
                   xend = xend,
                   yend = yend,
                   linetype = group,
                   group = group,
                   label = time),
               size = 3.5,
             curvature = 0.20,
             color = "black") +
  # Plot origins and destinations
  geom_point(data = od,
            aes(size = size,
                x = x, 
                y = y, 
                color = type,
                shape = type)) +
  scale_size(range = c(4, 10)) +
  # Label origins and destinations
  geom_text(data = od, 
            aes(x, 
                y, 
                label=id), 
            size=4) +
  # Create table
  annotate(geom = "table",
           x = 9, 
           y = 9, 
           label = list(od_table),
           fill = "white",
           size=3) +
  # Theme the plot
  coord_fixed() + 
  theme_void() + guides(shape = "none", size = "none", color = "none", linetype ="none")

@@

$$A_i^m = \sum_{j}O_jf(c_{ij})^m$$
-   $i$ is a set of origin locations
-   $j$ is a set of destination locations
-   $O_j$ is the number of opportunities at location $j$
-   $f(\cdot)$ is an impedance function of $c_{ij}$ (cost of moving between $i$ and $j$) for each mode $m$; if binary, the measure if _cumulative opportunities_

-- 
.pull-right[

**E.g.**, used in _(Tahmasbi et al., 2019)_ to calculate $A_i^m$ (per mode). Variations on how it is combined across modes.

@@

Does not include competition (demand:supply, mass effect) _(Shen, 1998; Merlin and Hu, 2018)_.

@@

@@

- Used in _(Tahmasbi et al., 2019)_ to quantify access $A_i$ for $m$ walking, public transit, and private car modes to retail store destinations (different $f^m(c_{ij}^m)$ for each $m$). Variations on how it is combined across modes (if at all) for general accessibility. It varies so widely because interpretation is inconsistent.
- Suffers from the same interpretability issues _(Handy and Niemeier, 1997; Miller et al., 2018)_
- Does not include competition (demand:supply or the mass effect) _(Shen, 1998; Merlin and Hu, 2018)_

---
## Multi-modal accessibility measures

.pull-left[
#### Competitive accessibility (Shen-type) - no proportional allocation
Shen (1998) modified Hansen-type accessibility; popularized as the **two-step floating catchment area (2SFCA) method** by _(Luo and Wang, 2003)_

@@

Generalized multi-model competition:
$$S_i = \sum_m \biggl(\frac{P_i^m}{P_i}\biggr) \sum_j \frac{O_jf(c_{ij})^m}{\sum_m \sum_i P_{i}^m f(c_{ij})^m}$$

@@

However, the resulting value is an accessibility _score_ so interpretation is obfuscated _(Soukhov et al., 2023)_.

@@

.right-column[
```{r comparison-impedance-functions-synthetic-example1, echo=FALSE, warning=FALSE, fig.width=8, fig.height=6}
data.frame(tt = seq(0, 100, 1)) %>%
  mutate(f1 = exp(-0.1 * tt)) %>%
  pivot_longer(cols = -tt,
               names_to = "Function",
               values_to = "f") %>%
  mutate(Function = case_when(Function == "f1" ~ "beta = 0.1")) %>%
  ggplot() +
  xlab(expression(c[ij]~"(travel time in minutes)")) +
  ylab(expression('f(c'[ij]*')')) +
  geom_line(aes(x = tt, 
                y = f,
                color = Function), size=1) +
  scale_color_manual(values = c("dark green"), label = c(expression("exp(-0.1 c"[ij]*")")))+
  scale_x_continuous(breaks = seq(0, 80, 20))+
  theme_minimal()+
  theme(axis.title = element_text(size=18),
        axis.text = element_text(size=16),
        legend.position = c(0.85, 0.9),
        legend.title = element_blank(),
        legend.text = element_text(size=18))
```
]

@@

.right-column[
```{r comparison-impedance-functions-synthetic-example2, warning=FALSE, echo=FALSE, fig.width=8, fig.height=6}
data.frame(tt = seq(0, 100, 1)) %>%
  mutate(f1 = exp(-0.1 * tt),
         f2 = exp(-0.6 * tt)) %>%
  pivot_longer(cols = -tt,
               names_to = "Function",
               values_to = "f") %>%
  mutate(Function = case_when(Function == "f1" ~ "beta = 0.1",
                              Function == "f2" ~ "beta = 0.6")) %>%
  ggplot() +
  xlab(expression(c[ij]~"(travel time in minutes)")) +
  ylab(expression('f(c'[ij]*')')) +
  geom_line(aes(x = tt, 
                y = f,
                color = Function), size=1) +
  scale_color_manual(values = c("dark green", "#9999CC"), label = c(expression("exp(-0.1 c"[ij]*")"), expression("exp(-0.6 c"[ij]*")")))+
  scale_x_continuous(breaks = seq(0, 80, 20))+
  theme_minimal()+
  theme(axis.title = element_text(size=18),
        axis.text = element_text(size=16),
        legend.position = c(0.85, 0.9),
        legend.title = element_blank(),
        legend.text = element_text(size=18))
```
]

$f(c_{ij}) = 1$ if $c_{ij} \leq 30$ else 
  $f(c_{ij}) = 0$

.right-column[
```{r comparison-impedance-functions-synthetic-example3, warning=FALSE, echo=FALSE, fig.width=8, fig.height=6}
data.frame(tt = seq(0, 100, 1)) %>%
  mutate(f1 = exp(-0.1 * tt),
         f2 = exp(-0.6 * tt),
         f3 = ifelse(tt < 30, 1, 0)) %>%
  pivot_longer(cols = -tt,
               names_to = "Function",
               values_to = "f") %>%
  mutate(Function = case_when(Function == "f1" ~ "beta = 0.1",
                              Function == "f2" ~ "beta = 0.6",
                              Function == "f3" ~ "tt <= 30")) %>%
  ggplot() +
  xlab(expression(c[ij]~"(travel time in minutes)")) +
  ylab(expression('f(c'[ij]*')')) +
  geom_line(aes(x = tt, 
                y = f,
                color = Function), size=1) +
  scale_color_manual(values = c("dark green", "#9999CC", "#CC6666"), label = c(expression("exp(-0.1 c"[ij]*")"), expression("exp(-0.6 c"[ij]*")"), expression(c[ij]~"< 30 min")))+
  scale_x_continuous(breaks = seq(0, 80, 20))+
  theme_minimal()+
  theme(axis.title = element_text(size=18),
        axis.text = element_text(size=16),
        legend.position = c(0.85, 0.9),
        legend.title = element_blank(),
        legend.text = element_text(size=18))
```
]
---
### Simulated example - Hansen-type accessibility (no competition or proportional allocation consideration)

@@

.pull-left[
```{r, echo=FALSE}
knitr::include_graphics("Presentations/toy-example.png")
```

@@

.pull-right[
$S_i = \sum_m \biggl(\frac{P_i^m}{P_i}\biggr) S_i^m$
```{r, echo=FALSE, message=FALSE}
S <- S_m %>%
  group_by(i) |>
  summarize(S = sum(pop*S)/sum(pop),
            .groups = "drop")

@@

- Spatial availability considering multi-modes:

$V^m_{i} = \sum_{j}^J O_j\ F^{t,m}_{ij}$

@@

- Total spatial availability: $V_{i} = \sum_{m}^M V^m_{i}$
  - Considers **competition** and **proportionally allocates opportunities** (singly-constrained: $O = \sum_{j} O_j$)

- Total spatial availability per capita: $v_{i} = \sum_{m} \frac{V_i^m}{P_{i^m}}$
  - Equivalent to Shen-style accessibility

???
- So let me introduce spatial availability, it consists of proportional allocation factors and the opportunities. the population allocation factor is the allocation of opportunities, proportional to the population size. It is always a proportion between 0 to 1.

@@

$V^m_{i} = \sum_{j} O_j\ F^{t,m}_{ij}$ and $v^m_{i} = \frac{V^m_{i}}{P_{i}^m}$

@@

.pull-right[
$S_i$ (eqv. to $v_i$) and $V_{i} = \sum_{m=1}^M V^m_{i}$

@@

.pull-left[
```{r, echo=FALSE, out.width='120%',fig.align='center'}
knitr::include_graphics("Presentations/SA_i_V_zn1259_plot.png")
```
Spatial Availability $V_i$ at resolution Zona 1259
]

.pull-right[
```{r, echo=FALSE, out.width='120%', fig.align='center'}
knitr::include_graphics("Presentations/SA_i_V_zn208_plot.png")
```
Spatial Availability $V_i$ at resolution Zona 208
]

@@

---
class: center
### Multi-modal home-to-work accessibility in Madrid: 2018 travel survey
```{r, echo=FALSE, out.width='45%',fig.align='center'}
knitr::include_graphics("Presentations/SA_im_vv_zn1259_plot.png")
```
Spatial Availability by $m$ population ( $v_i^m$ ) at resolution Zona 1259

@@

---
class: center, middle, inverse

#Extra slides

---
### Proof: Spatial availability cancels out into Shen-style accessibility

Population allocation factor:
$F^p_{ij} = \frac{P_{i\in r}^\alpha}{\sum_{i}^K P_{i\in r}^\alpha}$

$F^p_{A} = \frac{P_{A}^\alpha}{P_{A}^\alpha + P_{B}^\alpha + P_{C}^\alpha}$

Cost allocation factor:
$F^c_{ij} = \frac{f(c_{ij})}{\sum_{i=A}^K f(c_{ij})}$

$F^c_{A1} = \frac{f(c_{A1})}{f(c_{A1})+f(c_{B1})+f(c_{C1})}$
$F^c_{B1} = \frac{f(c_{A2})}{f(c_{A2})+f(c_{B2})+f(c_{C2})}$
$F^c_{C1} = \frac{f(c_{A3})}{f(c_{A3})+f(c_{B3})+f(c_{C3})}$

Now let's put it together with P, and see how the denominators end up cancelling out:
$v_{i} = \sum_{j}\frac{O_j}{P_{i\in r}^\alpha}\frac{\frac{P_{i\in r}^\alpha}{\sum_{i}^K P_{i\in r}^\alpha} \cdot \frac{f(c_{ij})}{\sum_{i}^K f(c_{ij})}}{\sum_{i}^K \frac{P_{i\in r}^\alpha}{\sum_{i}^K P_{i\in r}^\alpha} \cdot \frac{f(c_{ij})}{\sum_{i}^K f(c_{ij})}}$

- we presented this formula to a few accessibility academics and because the way we explained it - from the perspective of proportional allocation - made it appear to be different than shen's. It was a surprise to see the denominators cancel out to equal shen's!

---

$v_{A} = \frac{O_1}{P_{A}^\alpha}(\frac{\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{A1})}{f(c_{A1})+f(c_{B1})+f(c_{C1})}}{\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{A1})}{f(c_{A1})+f(c_{B1})+f(c_{C1})} + \frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{B1})}{f(c_{A1})+f(c_{B1})+f(c_{C1})}+ \frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{C1})}{f(c_{A1})+f(c_{B1})+f(c_{C1})}}) +$

$\frac{O_2}{P_{A}^\alpha}(\frac{\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{A2})}{f(c_{A2})+f(c_{B2})+f(c_{C2})}}{\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{A2})}{f(c_{A2})+f(c_{B2})+f(c_{C2})} + \frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{B2})}{f(c_{A2})+f(c_{B2})+f(c_{C2})}+\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{C2})}{f(c_{A2})+f(c_{B2})+f(c_{C2})}} )+$

$\frac{O_3}{P_{A}^\alpha}(\frac{\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{A3})}{f(c_{A3})+f(c_{B3})+f(c_{C3})}}{\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{A3})}{f(c_{A3})+f(c_{B3})+f(c_{C3})} + \frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{B3})}{f(c_{A3})+f(c_{B3})+f(c_{C3})}+\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{C3})}{f(c_{A3})+f(c_{B3})+f(c_{C3})}} )$

First, notice how the denominator on the denominator is the same across the summation? Let's simplify it:

$v_{A} = \frac{O_1}{P_{A}^\alpha}(\frac{\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{A1})}{f(c_{A1})+f(c_{B1})+f(c_{C1})}}{\frac{P_{A}^\alpha \cdot f(c_{A1}) + P_{A}^\alpha \cdot f(c_{B1}) + P_{A}^\alpha \cdot f(c_{C1})}{(P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha) \cdot (f(c_{A1})+f(c_{B1})+f(c_{C1}))}}) +$
$\frac{O_2}{P_{A}^\alpha}(\frac{\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{A2})}{f(c_{A2})+f(c_{B2})+f(c_{C2})}}{\frac{P_{A}^\alpha \cdot f(c_{A2}) + P_{A}^\alpha \cdot f(c_{B2}) + P_{A}^\alpha \cdot f(c_{C2})}{(P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha) \cdot (f(c_{A2})+f(c_{B2})+f(c_{C2}))}}) +$
$\frac{O_3}{P_{A}^\alpha}(\frac{\frac{P_{A}^\alpha}{P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha} \cdot \frac{f(c_{A3})}{f(c_{A3})+f(c_{B3})+f(c_{C3})}}{\frac{P_{A}^\alpha \cdot f(c_{A3}) + P_{A}^\alpha \cdot f(c_{B3}) + P_{A}^\alpha \cdot f(c_{C3})}{(P_{A}^\alpha+P_{B}^\alpha+P_{C}^\alpha) \cdot (f(c_{A3})+f(c_{B3})+f(c_{C3}))}} )$

See how the denominator of the denominator is the same as the denominator of the numerator's denominator for each J (J=1, J=2, and J=3)? Let's cancel those out and simplify:

$v_{A} = \frac{O_1}{P_{A}^\alpha}(\frac{P_{A}^\alpha \cdot f(c_{A1})}{P_{A}^\alpha \cdot f(c_{A1}) + P_{A}^\alpha \cdot f(c_{B1}) + P_{A}^\alpha \cdot f(c_{C1})} +$
$\frac{O_2}{P_{A}^\alpha}\frac{P_{A}^\alpha \cdot f(c_{A2})}{P_{A}^\alpha \cdot f(c_{A2}) + P_{A}^\alpha \cdot f(c_{B2}) + P_{A}^\alpha \cdot f(c_{C2})} +$
$\frac{O_3}{P_{A}^\alpha}\frac{P_{A}^\alpha \cdot f(c_{A3})}{P_{A}^\alpha \cdot f(c_{A3}) + P_{A}^\alpha \cdot f(c_{B3}) + P_{A}^\alpha \cdot f(c_{C3})} )$

---

Next, see how we can cancel out the $P_{A}^\alpha$? Let's do that.

$v_{A} = O_1(\frac{f(c_{A1})}{P_{A}^\alpha \cdot f(c_{A1}) + P_{B}^\alpha \cdot f(c_{B1}) + P_{C}^\alpha \cdot f(c_{C1})} + O_2\frac{f(c_{A2})}{P_{A}^\alpha \cdot f(c_{A2}) + P_{B}^\alpha \cdot f(c_{B2}) + P_{C}^\alpha \cdot f(c_{C2})} + O_3\frac{f(c_{A3})}{P_{A}^\alpha \cdot f(c_{A3}) + P_{B}^\alpha \cdot f(c_{B3}) + P_{C}^\alpha \cdot f(c_{C3})} )$

```{r, eval=FALSE, include=FALSE}
#Let's check to see if it manually adds up to what shen's is
b<-0
r1 <- 100000*exp(-b*15)/(50000*exp(-b*15) + 150000*exp(-b*30) + 10000*exp(-b*100))
r2 <-100000*exp(-b*30)/(50000*exp(-b*30) + 150000*exp(-b*15) + 10000*exp(-b*100))
r3 <- 10000*exp(-b*100)/(50000*exp(-b*100) + 150000*exp(-b*100) + 10000*exp(-b*15))
r1+r2+r3

#this is shen's, the same!!!
j1<-(100000*exp(-0.1*15))/(50000 * exp(-b * 15) + 150000 * exp(-b * 30) + 10000 * exp(-b * 100))
j2<-(100000*exp(-0.1*30))/(50000 * exp(-b * 30) + 150000 * exp(-b * 15) + 10000 * exp(-b * 100))
j3<-(10000*exp(-0.1*100))/(50000 * exp(-b * 100) + 150000 * exp(-b * 100) + 10000 * exp(-b * 15))
j1 + j2 + j3
```
```{r, eval=FALSE, include=FALSE}
(exp(-b*15)/((50000*exp(-b*15)) + (50000*exp(-b*30)) + (50000*exp(-b*100)))+ exp(-b*30)/((50000*exp(-b*15)) + (50000*exp(-b*30)) + (50000*exp(-b*100)))+ exp(-b*100)/((50000*exp(-b*15)) + (50000*exp(-b*30)) + (50000*exp(-b*100))))*100000
```

Shen's accessibility:

$S_i = \sum_j \frac{O_jf(c_{ij})}{\sum_kP_kf(c_{jk})}$

---
